Who Needs Privacy? Exploring the relationship between personality and need for privacy

### 2021-10-25 analyses.RmD
- finished first rough overhaul of introduction and methods

To estimate sample size, we conducted a rudimentary power analysis. That is, we planned for a two-sided correlation of r = .1. We adopted a balanced alpha and beta error approach. Because we were in exploration mode, we aimed for a high statistical power and relaxed alpha. Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget. Instead, we opted for an error rate of 10%.

@@

# a priori power analyses
pwr.r.test(r = sesoi, sig.level = .05, power = .95) ## too expensive
```

@@

```{r}
pwr.r.test(r = sesoi, sig.level = .1, power = .9)
```

@@

```{r}
power <- pwr.r.test(r = sesoi, sig.level = .05, power = .8)
print(power)
power_n <- power$n
```

>>>>

To estimate sample size, we conducted a rudimentary power analysis. That is, we planned for a two-sided correlation of _r_ = .1. We adopted a balanced alpha and beta error approach. Because we were in "exploration mode", we aimed for a high statistical power and hence relaxed alpha. Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget. Instead, we opted for an error rate of 10%.

@@

# a priori power analyses
pwr.r.test(r = sesoi, sig.level = .05, power = .95) ## too expensive
power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
```

@@

```{r}
pwr.r.test(r = sesoi, sig.level = .1, power = .9)
power_n_90 <- pwr.r.test(r = sesoi, sig.level = .1, power = .9)$n
```

@@
